---
title: "Map"
runtime: shiny
output: 
        flexdashboard::flex_dashboard:
        source_code: embed
        theme: united

---

```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(mapview)
library(rgdal)
library(sf)
library(tidyverse)
library(ggthemes)
library(viridis)
library(rnaturalearth)
library(hrbrthemes)
library(patchwork)
library(RColorBrewer)
library(lwgeom)
library(units)
library(shiny)


##
ltem <- readRDS("")


sites_year <- ltem %>%
  group_by(Year,IDReef, Reef, Depth) %>%
  summarise(Transects= length(unique(Transect)),
            Species_n=sum(Quantity),
            Latitude=unique(Latitude),
            Longitude=unique(Longitude)
            
  ) %>%
  group_by(IDReef, Reef,Depth) %>% 
  summarise(
            Years= list(unique(Year)),
            Total_years= length(unique(Year)),
            Transects=Transects,
            Species_n=Species_n,
            Latitude=Latitude,
            Longitude=Longitude)
sites_year <- st_as_sf(sites_year, coords = c("Longitude", "Latitude"), crs = 4326)
```


```{r}

sites_year$labels1 <- paste0(
  "<h3 style= 'background-color:#87683a; color: white; text-align: center; font-size: 140%; font-family:Times New Roman'> Sitio </h3>", 
                     "<b style= 'color:#263270'> Depth: </b> ", sites_year$Depth, "<br/> ",
                     "<b style= 'color:#263270'> Years: </b> ", sites_year$Total_years, "<br/> ",
   "<b style= 'color:#263270'> Total Years: </b> ", sites_year$Years, "<br/> ",
                     "<b style= 'color:#263270'> Transects: </b> ", sites_year$Transects, "<br/> ",
                     "<b style= 'color:#263270'> Species: </b> ", sites_year$Species_n, "<br/> ") %>%
        lapply(htmltools::HTML)


leaflet(sites_year) %>%
        addProviderTiles(providers$Esri.WorldImagery, group = "Satélite") %>%
        addProviderTiles(providers$Esri.WorldTopoMap, group = "Mapa") %>%
        addProviderTiles(providers$Esri.OceanBasemap, group = "Océano") %>%

        setView(lat = 23.8497874,
                lng = -109.3884183,
                zoom = 30) %>%
        addMarkers(
                popup = ~ labels1,
                group = "Sitios"
                
        )  %>% 
        # Layers control
        addLayersControl(
                baseGroups = c("Satélite", "Mapa", "Ocean"),
                overlayGroups = c("Sitios"),
                options = layersControlOptions(collapsed = TRUE)
        ) %>%


    addMiniMap(
  position = "bottomright",
  width = 140,
  height = 140,
  collapsedWidth = 19,
  collapsedHeight = 19,
  zoomLevelOffset = -5,
  zoomLevelFixed = FALSE,
  centerFixed = FALSE,
  zoomAnimation = TRUE,
  toggleDisplay = TRUE,
  autoToggleDisplay = FALSE,
  minimized = FALSE,
  aimingRectOptions = list(color = "#ff7800", weight = 1, clickable = FALSE),
  shadowRectOptions = list(color = "#000000", weight = 1, clickable = FALSE, opacity =
    0, fillOpacity = 0),
  strings = list(hideText = "Hide MiniMap", showText = "Show MiniMap"),
  tiles = NULL,
  mapOptions = list()
)








